\textsf{Are large language models superhuman chemists?}

### 2024-10-29 src/tex/appendix.tex
recompile

\oone consistently leads across both the \ChemBench corpus and \chembenchmini.  \ClaudeThreeFiveSonnet, \GPTFourO, \LlamaThreeOneFourZeroFiveBInstruct form the next tier of strong performers. These models show robust performance across all skills and difficulty levels.

Larger models generally perform better (\LlamaThreeOneFourZeroFiveBInstruct > \LlamaThreeOneSeventyBInstruct > \LlamaThreeOneEightBInstruct). However, smaller but well-designed models can compete with larger models. For example, \GemmaTwoNineBIt has an overall accuracy of \variable{output/trends_section_variables/gemma_9B.txt} on the \ChemBench corpus, which is only \variable{output/trends_section_variables/diff_between_llama_405B_and_gemma_9B.txt}\% less accurate than the much larger \LlamaThreeOneFourZeroFiveBInstruct model.

>>>>

\oone consistently leads across both the \chembench corpus and \chembenchmini.  \ClaudeThreeFiveSonnet, \GPTFourO, \LlamaThreeOneFourZeroFiveBInstruct form the next tier of strong performers. These models show robust performance across all skills and difficulty levels.

Larger models generally perform better (\LlamaThreeOneFourZeroFiveBInstruct > \LlamaThreeOneSeventyBInstruct > \LlamaThreeOneEightBInstruct). However, smaller but well-designed models can compete with larger models. For example, \GemmaTwoNineBIt has an overall accuracy of \variable{output/trends_section_variables/gemma_9B.txt} on the \chembench corpus, which is only \variable{output/trends_section_variables/diff_between_llama_405B_and_gemma_9B.txt}\% less accurate than the much larger \LlamaThreeOneFourZeroFiveBInstruct model.
